% Glossary for sohn_topological_2011

\newglossaryentry{power-law}
{
  name=Power-law Degree Distributions,
  description={ Degree of distribution follows a power law (at least aymptotically):
	the fraction $ P(k) $ of nodes in the network having k connections to other nodes goes for large values of k as
	$$ P(k) \sim k^{- \gamma} $$
	A scale-free network follows such degree distribution.
  }
  % Introduction
}

\newglossaryentry{local-motif}
{
  name=Local Motif,
  description={ Or network motif: "patterns of interconnections occuring in complex networks at numbers
  	that are significantly higher than those in randomized networks.
  }
  %Introduction
}

\newglossaryentry{modularity-community}
{
  name=Modularity-based Community Detection,
  description={ From paper: Community structure in directed networks
	(doi: doi:10.1371/journal.pone.0037292)
	and Finding community structure in very large networks (Clauset et al)
  }
  %Introduction
}

\newglossaryentry{annealing}
{
  name=Simulated Annealing,
  description={ A method of stochastic optimization:
	\href{run:../readings/Metropolis_hmc.pdf}{Simulated Annealing \& Metropolis Algorithm}
  }
  %Introduction
}

\newglossaryentry{variation-of-information}
{
  name=Variation of Information,
  description={ between two partitions $C$ and $C'$ is defined as follows:
  	$$ V(C, C') = V(X, Y) = H(X | Y) + H(Y | X) ,$$
  	where $X$ and $Y$ denote the vectors representing the cluster assignment of community divisions
  	$C$ and $C'$, respectively. $ H(X | Y) $ is the conditional entropy indicating the amount of 
  	additional information needed to describe $C$ given $C'$.
  }
  %Results
}

\newglossaryentry{dendrogram}
{
  name=Dendrogram,
  description={ Tree diagram frequently used to illustrate the arrangement of the clusters produced by
	hierarchical clustering.
  }
  %Results
}

\newglossaryentry{IQV}
{
  name=Index of Qualitative Variation,
  description={ measures the heterogeneity of composition in a cluster. High IQV scores for a cluster indicate that the cluster is composed of
various neuronal types or ganglionic neurons.
  }
  %Membership properties of structural clusters
}

\newglossaryentry{within-module-weight}
{
  name=Within Module Weight,
  description={ evaluates how strongly a neuron is connected to other neurons within its cluster. }
}

\newglossaryentry{participation-coefficient}
{
  name=Participation Coefficient,
  description={ quantifies how extensively the connections of a neuron are distributed among different clusters.
  }
}

\newglossaryentry{t-test}
{
  name=T-test,
  description={ any statistical hypothesis test in which the test statistic follows a Student's t distribution if the null hypothesis is
supported.
  }
  %Association between topological cluster and functional circuits
}



% Acronym ======================================================

\newacronym{iqv}{IQV}{Index of Qualitative Variation}
