
\section{C-Elegans} 
\label{section:c-elegans} 

Caenorhabditis elegans (pron.: /ˌseɪnɵræbˈdɪtɪs ˈɛlɛɡænz/) is a free-living, transparent nematode (roundworm).

\begin{itemize}
  \item Size: about 1mm in length
  \item Number of neurons: 
    It is one of the simplest organisms with a nervous system. In the hermaphrodite, this comprises 302 neurons whose pattern of connectivity, or "connectome", has been
    completely mapped and shown to be a \href{http://en.wikipedia.org/wiki/Small-world-network}{small-world network}.
  \item Number of synapses: 7000
  \item Sex: C-elegans has two sexes: hermaphrodites and males. Sex in C. elegans is based on an X0 sex-determination system.

  {\tt http://worms.aecom.yu.edu/}
\end{itemize}

\subsection{Clustering}
To perform natural computation efficiently: specialized modules with locally dense connections

\paragraph{Significance} of the existence of clusters: organization of functional modules.Ganglion vs. synaptic connection;
Topological nature of the structure plays an important role in the information processing of C-elegans network.

\paragraph{C-elegans wiring}
5 anatomical clusters in the C-elegans eonnectome, which correspond to experimentally-identified functional circuits.
cooperation including mechanosensation, chemosensation and navigation

\subsubsection{complex network analysis}
Brain: small-world topology from microscopic level (eg. that of C-elegans)
Scale-free degree distribution
structural and functional motifs
Robustness and fragility of brain structural networks with respect to lesions and diseases

Determination and characterization of hierarchical sluster structure: densely connected groups of nodes with sparser connections among groups
Topological clusters in brain structure may correspond to sets of distinct anatomical modeules of neurons.

\subsubsection{method} 
Modularity-based community detection algorithm for directed weighted networks. (modularity maximizatio approach)
\paragraph{Modularity}
is a quantitative measure defined as the number of edges falling within groups minus the expected number in an equivalent network with edges placed at random.
The modularity value $Q$, indicates the degree to which a given paritition maximizes intra-cluster weights and minimizes inter-cluster weights. Define:
$Q=\frac{1}{4W} s^{T}(B + B^{T})s,$ \\
$B_{ij} = A_{ij} - \frac{S_i^{in} S_j^{out}}{W} $ \\
$B_{ij}$: the extent to which the connections from j to i are prominent. \\
$W = \sum_{ij} A_{ij} = \sum_i S_i^{in} = \sum_i S_i^{out}$
\\
Postive values demonstrate the possible presence of cluster structure.

\paragraph{Complexity}:
 NP-complete; approximation heuristics to obtain a near-optimal community assignment vector.
Constraints for C-elegans: information given by bilateral functional symmetry of the neuron cells.
Simulated annealing method: a generic probabillistic metaheuristic for the global optimization problem of locating a good approximation to the global optimum of a given
function in a large search space.

Prior knowledge: to reduce the number of community assignment vectors
bilateral nuronal pairs have similar functional roles, accepting the principle of structure-function association in evolutionary biology.

Spectral detection; fast unfolding.

\subsubsection{graph model}
Degree: number of synaptic partner neurons of a neuron
Weight: appropriate sum of synapses between specific neuronal partners
Strength: total weights of synaptic connections afferent to or eferent from a neuron.

\subsubsection{result}
\begin{quote}{While C. elegans
neurons are spatially concentrated in a manner related to their
ganglionic affiliation, we failed to observe a strong spatial
localization of neurons belonging to the same cluster, except for
those in clusters 11 and 12.}
\end{quote}

\paragraph{Hierarchical relationship}
of clusters is shown from the reordered adjacency matrix of C-elegans connectome.

\paragraph{Index of Qualitative Variation} measures the diversity of types of ganglia in one cluster. 4 of 5 clusters did not display dominant neurotransmitter type.
Low level of correlation between ganglia and cluster assignment.

\paragraph{Functional Cartography}
\begin{itemize}
  \item within-module weight
  \item participation coefficient
\end{itemize}
Characterize each neuron as either provincial or peripheral node, a hub, or a node with few within-module degrees. The types of nodes have a correlation with the types
of neurons.

\paragraph{Use in Complex Behaviors}
Hub Cluster: outward synapses to clusters having many inward synapses;
authoritative clusters have inward synapses from clusters that bridge to them through outward synapses.

\begin{quote}{Thus, the body-spanning cluster 22, whose members are
predominantly motor neurons, acted as an ‘authority’ receiving
information from hub clusters to produce consequential behaviors.}
\end{quote}

\begin{quote}{the structural clusters indentified in
this study appear to serve as a cohesive sub-module for
information processing at various stages.}
\end{quote}

\subsubsection{Present Constraints}
\begin{itemize}
  \item The lack of more appropriate model about inhibitory / excitatory sysnapses (some paper makes rough guess of the signs of synapses based on neurotransmitter gene
expression data.)
  \item Directionality for gap junctions (even if it existed) cannot be extracted from electron micrographs.
  \item When a presynaptic terminal makes contact with two adjacent processes of different neurons, it is not known which of these processes acts as a postsynaptic
terminal; both might be involved.
\end{itemize}

\subsubsection{Ref}
\url{web.mit.edu/lrv/www/elegans/}  provides information about algorithmic approach to analyzing C-elegans neuronal network data.
\url{www.wormatlas.org/ver1/MoW_built0.92/toc.html}  structure of the nervous system of C-elegans

\input{spectral-C-elegans}

\input{touch-circuit}

\newpage

\input{work/06-18-2013}

\input{C-elegans-data/male-wiring-data}
